R Notebook

### 2022-04-14 group-e/group-e-analysis.Rmd
improved gitignore to ignore pdfs and pngs in figure-latex

---
title: "R Notebook"
output: html_notebook
---

```{r}
library(dplyr)
library(tidyr)
library(jsonlite)
library(ggplot2)
```

@@

```{r}
attractiveness.curve <- summary.gaze.view %>% filter(roundness_task == FALSE)
fit <- nls(prop.in.target ~ MaxP + (MinP - MaxP)/(1+(time.window/InfP)^Slope), data = attractiveness.curve, start=list(MaxP=0.9,MinP=0.5,InfP=-500,Slope=-1))
```

>>>>

---
title: "R Notebook"
output:
  pdf_document: default
  html_notebook: default
---

```{r}
library(dplyr)
library(tidyr)
library(jsonlite)
library(ggplot2)
library(lme4)
```

@@

```{r}
attractiveness.curve <- summary.gaze.view %>% filter(task != "Roundness")
fit <- nls(prop.in.target ~ MaxP + (MinP - MaxP)/(1+(time.window/InfP)^Slope), data = attractiveness.curve, start=list(MaxP=0.9,MinP=0.5,InfP=-500,Slope=-1))
```
